### 2019-05-17 doc/bilevel/paper.tex
updates to bilevel
Updates to include a new pyomo example for bilevel

The \code{pao} package uses the \code{SubModel} component in \code{pyomo} to declare a block that defines a lower-level problem. 
For example, consider the bilevel problem:
\begin{equation}
\label{eqn:bilevel_ex1}
\begin{array}{ll}
\min_{v \in [1,2], x \in [1,2]}   & v + x + y\\
\st                 & x + v \geq 1.5\\
                    & y \in P(v,x)
\end{array}
\end{equation}
where 
\[
\begin{array}{llll}
P(v,x) & = & \argmin_{w \in [-1,1], y \in [1,2]}    & x + w\\
 & &                            &  y + w \leq 2.5
\end{array}
\]
which can be represented in \code{pao} as:

@@

model.o = Objective(expr=model.x + model.sub.y + model.v, sense=minimize)
model.c = Constraint(expr=model.x + model.v >= 1.5)
model.sub.o = Objective(expr=model.x+model.sub.w, sense=maximize)
model.sub.c = Constraint(expr=model.sub.y + model.sub.w <= 2.5)
\end{qlisting}
This Pyomo model defines four variables, \code{x}, \code{v}, \code{sub.y} and \code{sub.w}.
Variables \code{x} and \code{v} are declared in the upper-level
problem, and \code{v} only appears in the upper-level problem.
Variables \code{sub.y} and \code{sub.w} are declared in the submodel.
However, note that the \code{sub.y} variable appears in the upper-level
problem, while the \code{sub.w} variable only appears in the
lower-level problem.

@@

model.sub.o = Objective(expr=model.x + model.sub.w, sense=maximize)
model.sub.c = Constraint(expr=model.sub.y + model.sub.w <= 2.5)
\end{qlisting}

@@

>>>>

The \code{pao} package uses the \code{SubModel} component in \code{pyomo} to declare a block that defines a lower-level problem. 
For example, consider the bilevel problem:
\begin{equation}
\label{eqn:bilevel_ex1}
\begin{array}{ll}
\min_{v \in [1,2], x \in [1,2]}   & v + x + y\\
\st                 & v + x\geq 1.5\\
                    & y \in P(v,x)
\end{array}
\end{equation}
where 
\[
\begin{array}{llll}
P(v,x) & = & \argmin_{w \in [-1,1], y \in [1,2]}    & x + w\\
 & &                            &  y + w \leq 2.5
\end{array}
\]
which can be represented in \code{pao} as:

@@

model.o = Objective(expr=model.x + model.sub.y + model.v, sense=minimize)
model.c = Constraint(expr=model.x + model.v >= 1.5)
model.sub.o = Objective(expr=model.x+model.sub.w, sense=maximize)
model.sub.c = Constraint(expr=model.sub.y + model.sub.w <= 2.5)
\end{qlisting}
This Pyomo model defines four variables,  \code{v}, \code{x}, \code{sub.w} and \code{sub.y}.
Variables \code{v}  and \code{x} are declared in the upper-level
problem, and \code{v} only appears in the upper-level problem.
Variables \code{sub.w} and \code{sub.y} are declared in the submodel.
However, note that the \code{sub.y} variable appears in the upper-level
problem, while the \code{sub.w} variable only appears in the
lower-level problem.

@@

model.sub.o = Objective(expr=model.x + model.sub.w, sense=maximize)
model.sub.c = Constraint(expr=model.sub.y + model.sub.w <= 2.5)
\end{qlisting}
QUESTION: Is the last line correct here???\\

@@

\subsection{Using New Pyomo Notation}

For example, consider the bilevel problem:
\begin{equation}
\label{eqn:bilevel_ex1}
\begin{array}{ll}
\min_{v \in [1,2], x \in [1,2]}   & v + x + y\\
\st                 & v + x\geq 1.5\\
                    & y \in P(v,x)
\end{array}
\end{equation}
where 
\[
\begin{array}{llll}
P(v,x) & = & \argmin_{w \in [-1,1], y \in [1,2]}    & x + w\\
 & &                            &  y + w \leq 2.5
\end{array}
\]
which can be represented in \code{pao} pseudo-code as:

\begin{qlisting}
from pyomo.environ import *
import pyomo.kernel as pmo
from pao.bilevel import *
model = ConcreteModel()
model.x = Var(bounds=(1,2))
model.v = Var(bounds=(1,2))
model.y = Var(bounds=(1,2))
model.w = Var(bounds=(-1,1))
model.upper = SubModel(vars=[model.x,model.v])
model.lower = SubModel(vars = [model.y,model.w], parent = upper, 
		type = optimistic, argmin = model.y)

model.upper = Objective(expr=model.x + model.y + model.v, sense=minimize)

model.o = Objective(expr=model.x + model.y + model.v, sense=minimize)
model.c = Constraint(expr=model.x + model.v >= 1.5)
model.lower.o = Objective(expr=model.x+model.w, sense=maximize)
model.lower.c = Constraint(expr=model.y + model.w <= 2.5)
\end{qlisting}

\noindent PROS
\begin{itemize}
\item Requiring that each level of the problem be defined in a SubModel() block, which enables each submodel to be solved independently
\item The user must specify important aspects about that level of the problem when instantiating the SubModel()
\end{itemize}
CONS
\begin{itemize}
\item Implicitly fixes the vars not specified in the vars argument to the SubModel() to their current value
\item Variables have to be defined prior to instantiating the submodel; the user may want to define these on the SubModel() block
\end{itemize}
